---
title: "Eviction Dashboard"
author:
  - Thomas Gao, Intern
  - Open Justice Oklahoma
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
library(ojo)
library(knitr)


nc <- function(x) {comma(x, digits = 0)}

### Plaintiff cleaning function
windex <- function(x) {
  str_remove_all({{x}}, " INC| CO(?=($| ))|LLC|LP|LIMITED PARTNERSHIP|QLA|[[:punct:]]|THE | PHASE.{1,30}$|COMPANY|C\\/O.{1,30}| (AT|OF)(?= )| AND|II|DBA.*") %>% 
    str_replace_all("APT([[:alpha:]]|)|APARTMENT([[:alpha:]]|)$|APARTMENT HOMES", "APARTMENTS") %>% 
    str_replace("MHC|MHP|MOBILE HOME.*", "MOBILE HOMES") %>% 
    str_remove_all(" [[:alpha:]]$") %>% 
    str_squish %>%
    str_replace("HOUSING AUTH.*", "TULSA HOUSING AUTHORITY") %>% 
    str_replace("MENTAL HEALTH AS.*", "MENTAL HEALTH ASSOCIATION") %>% 
    str_replace("CHAT.*68.*", "CHATEAU 68 APARTMENTS") %>% 
    str_replace("J A AVONDALE", "JA AVONDALE")
}

windex_cleve <- function(x) {
  str_remove_all({{x}}, " INC| CO(?=($| ))|LLC|LP|LIMITED PARTNERSHIP|QLA|[[:punct:]]|THE | PHASE.{1,30}$|COMPANY|C\\/O.{1,30}| (AT|OF)(?= )| AND|II|DBA.*") %>% 
    str_replace_all("APT([[:alpha:]]|)|APARTMENT([[:alpha:]]|)$|APARTMENT HOMES", "APARTMENTS") %>% 
    str_remove_all(" [[:alpha:]]$") %>% 
    str_squish %>%
    str_replace("COUNTRY CREEK APARTMENTS", "COUNTRY CREEK") %>% 
    str_replace(".*CROSS TIMBER.*", "CROSS TIMBERS APARTMENTS")
}

```

Background information: Why are we researching this topic? What is the expected product? A blog post? Analysis for an internal or external partner?

> **What are the top 10 evictors in Oklahoma's top four most populous counties? (Tulsa, Oklahoma, Cleveland, Canadian)**

> **Approximately how many evictions were filed in each court from 2018-2019?**
> **Approximately how many different plaintiffs filed evictions in each court?**
> **What percentage of filers accounted for 50 percent of the evictions?**


# Data sources
OSCN small claims database

## Timeframe

Cases filed in 2018 and 2019

## Geography
Oklahoma's four most populous counties:
- Oklahoma
- Tulsa
- Cleveland
- Canadian
Tulsa county, Oklahoma county, maybe Cleveland and Canadian county

## Variables

What variables did you use? What types of cases, crimes, etc.?
iss_description Forcible entry and detainer
## Query

If you're using data from the OJO database, include the query you used to pull your data. This may be a function that starts `ojo_query_` or `dbGetQuery`.
###This step queries all the small claims court data from the 4 counties into a data frame 
``` {r}
okevic <- ojo_query_disps(c("TULSA", "OKLAHOMA", "CLEVELAND", "CANADIAN"), "SC", 2018:2019)
```

# Checking Data

Explain the results of the checks of your data.

## Check for Completeness

If you're using court data, you can use the `ojo_check_comp` to see how complete the data is.
###this step checks the completeness of the data 
```{r}
ojo_check_comp(okevic)
```

## Check for NAs

Detail the NAs and blank items in your data and, if necessary and possible, fill them in.
###this step filters out the dispositions without a defendant name
``` {r}
nas <- okevic %>% 
  group_by(casenum) %>% 
  filter(all(is.na(defname)| defname ==""))
```

## Check for outliers

If you're looking at numeric data, look at the highest and lowest values and explain your procedures to deal with them in this section.

# Defining Measures

This is where you'll likely spend the biggest chunk of time if you're using court data. There are a lot of ways things can go wrong, so we want to be able to trace back all of our steps and document all the decisions we're making.

Because each analysis project is a bit different, the number and length of subsections in this section will vary a lot. 
### this step will give us a list of issues filed in the small claims courts
```{r}
okevic %>% 
  count(iss_desc) %>% 
  arrange(desc(n))

### this step filters out only the eviction cases from the data frame

okevict <- okevic %>% 
  filter(str_detect(iss_desc, "FORCI"))

okevict %>% 
  count(iss_plaint) %>% 
  arrange(desc(n))

### this step changed the data frame from dispositions to actual cases by only saving one casenumber for each disposition 

okevict <- okevict %>% 
  group_by(court, casenum) %>% 
  slice(1)
```

### Fill plaintiff names for Cleveland County

``` {r}
cleve <- okevict %>% 
  filter(court == "CLEVELAND") %>% 
  select(-iss_plaint)

connect_ojo()
cleve_plaints <- dbGetQuery(ojo_db, "SELECT *
                            FROM oscn_party_names
                            WHERE court = 'CLEVELAND'
                            AND file_year > 2017
                            AND casetype = 'SC'")
disconnect_ojo()

cleve_plaints <- cleve_plaints %>% 
  filter(party_type == "Plaintiff") %>%
  group_by(court, casenum) %>% 
  slice(1) %>% 
  select(casenum, iss_plaint = party)

cleve <- cleve %>% 
  left_join(cleve_plaints)

okevict <- okevict %>% 
  filter(!court == "CLEVELAND") %>% 
  bind_rows(cleve)
  
```

Describe what you're looking for in each of these chunks

How many cases were filed in each court, 2018-2019?

This step gives us a break down of how many evictions were filed in each court from 2018-2019?

```{r}
year <- okevict %>% 
  ungroup %>% 
  count(court)

year
```
Who were the top evictors in each of these counties?
This step tells us how many evictions were filed in each court from 2018-2019? 

```{r}
plaintiff <- okevict %>% 
  ungroup %>% 
  count(court, iss_plaint) %>% 
  arrange(desc(n))

plaintiff
```

This step gives us who are the top 10 evictors in Oklahoma's top four most populous counties by cleaning the plaintiff names and counting how many cases they have filed and the data frame is then arranged in a descending order 

```{r}
tulsa <- okevict %>% 
  filter(court == "TULSA") %>% 
  mutate(plaint_clean = windex(iss_plaint))

tulsacount <- tulsa %>% 
  ungroup %>% 
  count(court, plaint_clean) %>% 
  arrange(desc(n)) %>% 
  group_by(court)

oklahoma <- okevict %>% 
  filter(court == "OKLAHOMA") %>% 
  mutate(plaint_clean = windex(iss_plaint))

oklahomacount <- oklahoma %>% 
  ungroup %>% 
  count(court, plaint_clean) %>% 
  arrange(desc(n)) %>% 
  group_by(court)

cleveland <- okevict %>% 
  filter(court == "CLEVELAND") %>% 
  mutate(plaint_clean = windex_cleve(iss_plaint))

clevelandcount <- cleveland %>% 
  ungroup %>% 
  count(court, plaint_clean) %>% 
  arrange(desc(n)) %>% 
  group_by(court)


canadian <- okevict %>% 
  filter(court == "CANADIAN") %>% 
  mutate(plaint_clean = windex(iss_plaint))

canadiancount <- canadian %>% 
  ungroup %>% 
  count(court, plaint_clean) %>% 
  arrange(desc(n)) %>% 
  group_by(court)


```
### this step calculates what percentage of evictors accounted for 50% of all eviction filings
```{r}
tulsacount

sum(tulsacount$n)/2

tulsacount <- tulsacount %>% 
  mutate(rank = row_number(),
        rolling_sum = cumsum(n))

totalcount1 <- merge(tulsacount, oklahomacount, by = c("court", "plaint_clean", "n"))
totalcount2 <- rbind(tulsacount, oklahomacount)
totalcount <- rbind(tulsacount, oklahomacount, clevelandcount, canadiancount)
sum(totalcount$n)/2
totalcount <- totalcount %>%
  ungroup %>% 
  arrange(desc(n)) %>% 
   mutate(rank = row_number(),
        rolling_sum = cumsum(n))

```

## Graph portion of evictions filed by top evictors

``` {r}
top_evictor <- totalcount %>% 
  mutate(top50percent = rank <= 240) %>% 
  group_by(top50percent) %>% 
  summarize(total_plaintiffs = n(),
            total_evictions = sum(n)) %>% 
  pivot_longer(cols = matches("total"),
               names_to = "figure")

ggplot(top_evictor, aes(figure, value, fill = top50percent)) +
  geom_bar(stat = "identity", position = "fill") +
  theme_ojo() +
  scale_fill_manual(values = ojo_pal) +
  ggtitle("Two percent of plaintiffs file half\nof all evictions")

```


# Summarizing and Visualizing Data

There will likely be several sections here too. Summarize and visualize the data in different ways and identify trends that you see.

## Summary 1

- How you summarized and why
- How you visualized the data
- Potential leads and trends

```{r results="asis", echo=FALSE}
cat("
<style>
body {
  padding-top: 63px;
}

h1.title.toc-ignore {
  font-family: 'Pluto Sans';
  font-weight: bold;
  background-color: #F8D64E;
}

h1, h2, h3 {
  font-family: 'Pluto Sans';
  font-weight: bold;
}

#TOC {
  font-family: 'Menlo'
}

.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    font-weight: bold;
    color: black;
    background-color: #F8D64E;
}

p a {
  color: black;
  background-color: #F8D64E;
  font-weight: bold;
}

</style>
")
```
