---
title: "Eviction Dashboard"
author:
  - Thomas Gao, Intern
  - Open Justice Oklahoma
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
library(ojo)
library(knitr)


nc <- function(x) {comma(x, digits = 0)}

```

Background information: Why are we researching this topic? What is the expected product? A blog post? Analysis for an internal or external partner?

> **What are the top 10 evictors in Oklahoma's top four most populous counties? (Tulsa, Oklahoma, Cleveland, Canadian)**

> **Approximately how many evictions were filed in each court from 2018-2019?**
> **Approximately how many different plaintiffs filed evictions?**
> **What percentage of filers accounted for 50 percent of the evictions?**


# Data sources
OSCN small claims database

## Timeframe

Cases filed in 2018 and 2019

## Geography
Oklahoma's four most populous counties:
- Oklahoma
- Tulsa
- Cleveland
- Canadian
Tulsa county, Oklahoma county, maybe Cleveland and Canadian county

## Variables

What variables did you use? What types of cases, crimes, etc.?
iss_description Forcible entry and detainer
## Query

If you're using data from the OJO database, include the query you used to pull your data. This may be a function that starts `ojo_query_` or `dbGetQuery`.

``` {r}
# d <- ojo_query_disps("TULSA", "CM", 2019)

okevic <- ojo_query_disps(c("TULSA", "OKLAHOMA", "CLEVELAND", "CANADIAN"), "SC", 2018:2019)
```

# Checking Data

Explain the results of the checks of your data.

## Check for Completeness

If you're using court data, you can use the `ojo_check_comp` to see how complete the data is.

```{r}
# ojo_check_comp(sc)
ojo_check_comp(okevic)
```

## Check for NAs

Detail the NAs and blank items in your data and, if necessary and possible, fill them in.

``` {r}
# rog_nas <- rog %>% 
#   summarize(nas = sum(is.na(defname) | defname == "")) # checks for NA and blank ("") defendant names
# 
# rog_nas
nas <- okevic %>% 
  group_by(casenum) %>% 
  filter(all(is.na(defname)| defname ==""))
```

## Check for outliers

If you're looking at numeric data, look at the highest and lowest values and explain your procedures to deal with them in this section.

# Defining Measures

This is where you'll likely spend the biggest chunk of time if you're using court data. There are a lot of ways things can go wrong, so we want to be able to trace back all of our steps and document all the decisions we're making.

Because each analysis project is a bit different, the number and length of subsections in this section will vary a lot. 
```{r}
okevic %>% 
  count(iss_desc) %>% 
  arrange(desc(n))
```
```{r}
okevict <- okevic %>% 
  filter(str_detect(iss_desc, "FORCI"))
```
```{r}
okevict %>% 
  count(iss_plaint) %>% 
  arrange(desc(n))
```
```{r}
okevict <- okevict %>% 
  group_by(casenum) %>% 
  slice(1)
```
```{r}
year <- okevict %>% 
  ungroup %>% 
  count(court)
```
```{r}
plaintiff <- okevict %>% 
  ungroup %>% 
  count(iss_plaint) %>% 
  arrange(desc(n))
```
```{r}
plaintcount <- okevict %>% 
  ungroup %>% 
  count(iss_plaint,court) %>% 
  arrange(desc(n)) %>% 
  group_by(court)
```



## Measure 1

Describe how you defined the first measure.

# Summarizing and Visualizing Data

There will likely be several sections here too. Summarize and visualize the data in different ways and identify trends that you see.

## Summary 1

- How you summarized and why
- How you visualized the data
- Potential leads and trends

```{r results="asis", echo=FALSE}
cat("
<style>
body {
  padding-top: 63px;
}

h1.title.toc-ignore {
  font-family: 'Pluto Sans';
  font-weight: bold;
  background-color: #F8D64E;
}

h1, h2, h3 {
  font-family: 'Pluto Sans';
  font-weight: bold;
}

#TOC {
  font-family: 'Menlo'
}

.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    font-weight: bold;
    color: black;
    background-color: #F8D64E;
}

p a {
  color: black;
  background-color: #F8D64E;
  font-weight: bold;
}

</style>
")
```
